Papers

### 2023-05-01 papers.qmd
update pdf
update
update papers

K. Rumsey, and J. G. Huerta, and **J. D. Tucker**, "A Localized Ensemble of Approximate Gaussian Processes for Fast Sequential Emulation", *Stat*, submitted, 2022.

**J. D. Tucker**, M. T. Martinez, and J. M. Laborde, "Dimensionality Reduction using Elastic Measures", *Stat*, 10.1002/sta4.551, 2023. [arxiv preprint](https://arxiv.org/abs/2209.04933)

J. Upston, D. Sulsky, **J. D. Tucker**, and Y. Guan, "CIEL\*Ch color map for visualization and analysis of sea ice motion", *Journal of Computational and Applied Mathematics*, 10.1016/j.cam.2023.115126, 2023. [PDF](Papers/1-s2.0-S0377042723000705-main.pdfupda)

>>>>

K. Rumsey, and J. G. Huerta, and **J. D. Tucker**, "A Localized Ensemble of Approximate Gaussian Processes for Fast Sequential Emulation", *Stat*, 10.1002/sta4.576, 2023. [PDF](Papers/leapGP23.pdf)

**J. D. Tucker**, M. T. Martinez, and J. M. Laborde, "Dimensionality Reduction using Elastic Measures", *Stat*, 10.1002/sta4.551, 2023. [PDF](Papers/Stat23.pdf)

J. Upston, D. Sulsky, **J. D. Tucker**, and Y. Guan, "CIEL\*Ch color map for visualization and analysis of sea ice motion", *Journal of Computational and Applied Mathematics*, 10.1016/j.cam.2023.115126, 2023. [PDF](Papers/1-s2.0-S0377042723000705-main.pdf)
